Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-12-16 demystify.tex
updates

Below are some tips to approach your LoR writers:
\begin{itemize}
\item \textbf{Ask in advance} You should ask for LoRs \emph{at least a month} before the deadline. People are busy and writing a strong LoR takes time (\autoref{sec:lor-writing}), so you should give them enough time to write a strong letter for you.

@@

\item \textbf{Ask for feedback} If the writer is very close to you, you can ask them for feedback on your application, e.g., your SOP.

\item \textbf{Follow up and Stay in touch} Follow up with your writers to make sure they have submitted the letters on time.  After your writers have submitted all of their letters, \emph{thank them}!  Finally, let them know the outcome of your applications and stay in touch with them.  This will help you build a relationship with them and you might need them to write for you again in the future.
\end{itemize}

@@

When you ask someone to write a letter for you, you will be asked if you want to waive your right to see the letter.  You should \emph{always} waive your right.

@@

\subsection{Help your LOR Writer}\label{sec:help-your-LOR-writers}

@@

\subsection{Remind Your Writers}\label{sec:remind-writers}

After entering your writers' information in the application system, you should tell your writers about that and let them know they will soon receive an email from the university to submit their letters.  You should also remind them when you submit your application and ask them to submit their letters on time if they haven't done so.

@@

\paragraph{Thank Your Writers} After your application is submitted and your writers have submitted their letters (i.e., the wait begins), you should send a quick thank you note, which serves both as an acknowledgement that you know they have submitted the letters and as an appreciate for their help.  You should also let them know the outcome of your application, regardless of whether you are admitted or not.  In addition to being a common courtesy, this can also help maintain a good relationship with your writers, which can be useful in the future (e.g., if you need another letter for another round of applications or for a job reference).

>>>>

Below are some tips to approach your LoR writers:
\begin{itemize}
\item \textbf{Ask in advance} You should ask for LoRs \emph{at least a month} before the deadline. People are busy and writing a strong LoR takes time (\autoref{sec:lor-writing}), so give them enough time to write a strong letter for you.

@@

\item \textbf{Ask for feedback} If the writer is very close to you, you can ask them for feedback on your SOP (\autoref{chap:sop}) and other application materials. If the writer is a professor, they might have served in adcom committees, seen many SOPs, and can provide valuable feedback.

\item \textbf{Follow up and Stay in touch} Follow up with your writers to make sure they have submitted the letters on time. Note that their letters might have a different due date than your application (\autoref{sec:remind-writers}).

After your writers have submitted all of their letters, \emph{thank them} (\autoref{sec:thank-writers}).  Finally, let them know the outcome of your applications and stay in touch with them.  This will help you build a relationship with them and you might need them to write for you again in the future.
\end{itemize}

@@

When you ask someone to write a letter for you, you should \emph{always} waive your right.

@@

\subsection{Helping your LOR Writer}\label{sec:help-your-LOR-writers}

@@

\subsection{Reminding Your Writers}\label{sec:remind-writers}

After entering your writers' information in the application system, you should tell your writers about that and let them know they will soon receive an email from the university to submit their letters.  You should also tell them when you submit your application and remind them to submit their letters on time if they haven't done so.

@@

\subsection{Thank Your Writers}\label{sec:thank-writers}
After your application is submitted and your writers have submitted their letters (i.e., the wait begins), you should send a quick thank you note, which serves both as an acknowledgement that you know they have submitted the letters and as an appreciate for their help.

You should also let them know the outcome of your application, regardless of whether you are admitted or not.  In addition to being a common courtesy, this can also help maintain a good relationship with your writers, which can be useful in the future (e.g., if you need another letter for another round of applications or for a job reference).
